---
title: "#tidytuesday Week 4 2020 - Spotify Songs"
output: github_document
---
[The Spotify Songs dataset](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-01-21/readme.md) contains data on over 30,000 songs available on the streaming service, Spotify. The dataset contains expected variables, such as the track name, artist and album - as well as assigned variables likely ranked by Spotify such as "danceability" and "acousticness". 

```{r Libraries & Data}
# Libraries
library(tidytuesdayR)
library(tidyverse)

# Data
tt_data <- tt_load(2020, week = 4); 
data <- tt_data$spotify_songs %>%
  select(-c(track_id, track_album_id, playlist_id)) %>%
  mutate(track_album_release_date = as.Date(track_album_release_date))

# EDA
data %>%
  count(playlist_genre)

data %>%
  count(playlist_subgenre)
```

## Ideas being considered:
- Music popularity over time
  - per genre

- Difference in song characteristics by genre

```{r Song characteristics}
names_characteristics <- data[,c(9:20)]

ggplot(data = data, mapping = aes(x = ))
```

## Music's popularity over time?